Algebraic File Synchronization: Adequacy and Completeness

### 2016-10-31 p2/ordering.tex
Continue with update detection

@@

\begin{mylem}\label{order_is_only_possible}
For any simple sequence $S$ and its permutation $T$, 
\[ T\not\in\orderset{S} \Longrightarrow T\equiv\cbrk. \]
\end{mylem}
\begin{proof}
TODO corollary
\end{proof}

@@

\begin{mylem}\label{simple_reorder_equiv}
For a simple sequence $S\nequiv\cbrk$,
\[ \orderset{S} = [S]_\equiv \cap \setssmp, \]
where $[S]_\equiv \cap \setssmp$ is the set of simple sequences equivalent to $S$.
\end{mylem}
\begin{proof}
First, we prove, by contradiction, that if a simple sequence $T\equiv S$, then $T\in\orderset{S}$.
We assume $T\equiv S$ and $T\not\in\orderset{S}$.
Then, from \cref{order_is_only_possible} we know $T\equiv\cbrk$ which
is a contradiction as $T\equiv S\nequiv\cbrk$.

@@

Let us consider $T\in\orderset{S}$ where $T$ and $S$ are of length $i+1$.
We note that for any subsequence of $S$, $S_0$, which contains
only part of the commands in $S$ but in the same order as in $S$,
and for the corresponding subsequence of $T$, $T_0$, which
contains the same commands but in the order they are found in $T$,
$T_0\in\orderset{S_0}$ must hold as
if there were no command pairs in $T$ not conforming to \cref{def_orderset},
then there cannot be any in $T_0$.

We also know that due to \cref{ax_separate_commute,incomparable_is_independent}
$T$ can be rearranged into $T'\equiv T$ where
$T'=T_1\cc T_2\cc \cdots \cc T_k$ and the segments $T_j$ are pairwise independent,
and where we have the maximum number of segments possible.
$S$ can be converted similarly into $S'$, and
as because of \cref{equiv_simple_same_commands} $S$ and $T$ contain the same commands,
the segments of $S'$ will contain the same commands as those of $T$.
Let us therefore rearrange the segments of $S'$ so that the first segment
$S_1$ would correspond to (i.e. contain the same commands as) $T_1$, the second segment $S_2$ to $T_2$,
and so on.

The segments contain commands in the same order as the full sequences.
Therefore, from the observation abvout subsequences
we know for all $1\leq j\leq k$, $T_j\in\orderset{S_j}$,
and if $T'$ has at least two segments and so 
they are shorter than $i+1$,
from the induction hypothesis
we also know $T_j\equiv S_j$, from which we get $T\equiv S$.

We can assume $T'$ has at least two commands,
and in the remaining case, when $T'$ has only one segment,
we know all nodes that the commands in $T'$ apply to
are related via $\descendant$.
$T'$ contains the same commands as $S$, and
from \cref{connected_changes} we see that the nodes the commands apply to therefore form a tree in $\setn$.
We can therefore select the command on the topmost node (let it be $\cxynv$),
and we know $T'$ contains commands on some of its child nodes.
Let one of these be $\czwmv$.
Now mark the command $\czwmv$ and all commands in $T'$ that are applied to nodes that are descendants of $m$.
From \cref{ax_separate_commute} we know that all remaining commands in $T'$ (except $\cxynv$)
commute with the marked commands; therefore we can swap them to get $T''\equiv T'$
where marked commands are next to $\cxynv$:
\[ T'' = T_\mathrm{unmarked\ left} \cc T_\mathrm{marked\ left} \cc \cxynv \cc T_\mathrm{marked\ right} \cc T_\mathrm{unmarked\ right}. \]

>>>>

\begin{mycor}\label{subseq_in_orderset}
For simple sequences $S$ and $T$,
if $T\in\orderset{S}$, then for any subsequence of $S$, $S_0$, which contains
only part of the commands in $S$ but in the same order as in $S$,
and for the corresponding subsequence of $T$, $T_0$, which
contains the same commands but in the order they are found in $T$,
$T_0\in\orderset{S_0}$ must hold.
\end{mycor}
\begin{proof}
This is because
if there are no command pairs in $T$ not conforming to \cref{def_orderset},
then there cannot be any in $T_0$.
\end{proof}

@@

\begin{mycor}\label{order_is_only_possible}
For any simple sequence $S$ and its permutation $S'$, 
\[ S'\not\in\orderset{S} \Longrightarrow S'\equiv\cbrk. \]
\end{mycor}
\begin{proof}
This follows directly from \cref{simple_distant_pairs}.
If $S'\not\in\orderset{S}$ then by \cref{def_orderset}
it contains two commands on a node $n$ and its parent
that placed next to each other do not form
a construction or destruction pair.
Let them be $\cxynv$ and $\czwmv$.
By \cref{ax_directchild_breaks,ax_directparent_breaks}
we know the subsequence of $S'$,
$\cxynv\cc\czwmv\equiv\cbrk$ and therefore by \cref{simple_distant_pairs}
$S'\equiv\cbrk$.
\end{proof}

@@

\begin{mylem}\label{simple_reorder_equiv}
For a simple sequence $S\nequiv\cbrk$,
\[ \orderset{S} = [S]_\equiv \cap \setssmp, \]
where $[S]_\equiv \cap \setssmp$ is the set of simple sequences equivalent to $S$.
\end{mylem}
\begin{proof}
First, we prove, by contradiction, that if a simple sequence $T\equiv S$, then $T\in\orderset{S}$.
We assume $T\equiv S$ and $T\not\in\orderset{S}$.
Then, from \cref{equiv_simple_same_commands} we know $T$ is a permutation of $S$,
and from \cref{order_is_only_possible} we know $T\equiv\cbrk$ which
is a contradiction as $T\equiv S\nequiv\cbrk$.

@@

Let us consider $T\in\orderset{S}$ where $T$ and $S$ are of length $i+1$.
We know that due to \cref{ax_separate_commute,incomparable_is_independent}
$T$ can be rearranged into $T'\equiv T$ where
$T'=T_1\cc T_2\cc \cdots \cc T_k$ and the segments $T_j$ are pairwise independent,
and where we have the maximum number of segments possible.
$S$ can be converted similarly into $S'$, and
as because of \cref{equiv_simple_same_commands} $S$ and $T$ contain the same commands,
the segments of $S'$ will contain the same commands as those of $T$.
Let us therefore rearrange the segments of $S'$ so that the first segment
$S_1$ would correspond to (i.e. contain the same commands as) $T_1$, the second segment $S_2$ to $T_2$,
and so on.

The segments contain commands in the same order as the full sequences.
Therefore, from \cref{subseq_in_orderset}
we know for all $1\leq j\leq k$, $T_j\in\orderset{S_j}$,
and if $T'$ has at least two segments and so 
they are shorter than $i+1$,
from the induction hypothesis
we also know $T_j\equiv S_j$, from which we get $T'\equiv S'$ and $T\equiv S$.

The remaining case is when $T'$ has at least two commands,
but only one segment, which means
that all nodes that the commands in $T'$ apply to
are related via $\descendant$.
$T'$ contains the same commands as $S$, and
from \cref{connected_changes} we see that the nodes the commands apply to therefore form a tree in $\setn$.
We can therefore select the command on the topmost node (let it be $\cxynv$),
and we know $T'$ contains commands on some of its child nodes.
Let one of these be $\czwmv$.
Now mark the command $\czwmv$ and all commands in $T'$ that are applied to nodes that are descendants of $m$.
From \cref{ax_separate_commute} we know that all remaining commands in $T'$ (except $\cxynv$)
commute with the marked commands; therefore we can swap them to get $T''\equiv T'$
where marked commands are next to $\cxynv$:
\[ T'' = T_\mathrm{unmarked\ left} \cc T_\mathrm{marked\ left} \cc \cxynv \cc T_\mathrm{marked\ right} \cc T_\mathrm{unmarked\ right}. \]
